PANCHANGE_data_preprocessing

### 2020-07-30 PANCHANGE_data_preprocessing2020-07-15.Rmd
PHQ retro and prepan missingness per person chunks

##Missigness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count and percentages
```{r Missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
           %in%
             phq.items_base]
        )
    )
  )

@@

>>>>

##Missigness of questionnaire items
#PHQ - baseline
PHQ Missingness NAs per person - count and percentages
```{r PHQ basline missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_base =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at baseline
           %in%
             phq.items_base]
        )
    )
  )

@@

#PHQ - retrospective
PHQ Missingness NAs per person - count and percentages
```{r PHQ retrospective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_retro =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at retroline
           %in%
             phq.items_retro]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_retro) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_retro = 
      na_per_person_phq_retro/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_retro)
```

#PHQ - prepanspective
PHQ Missingness NAs per person - count and percentages
```{r PHQ prepanspective missingness}
dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>%
  mutate(
    na_per_person_phq_prepan =         # variable for NA per person
      rowSums(                       
        is.na(dat.no.sex.no.gender.no.age.no.ibd # sum the rows that are NA
          [,colnames(dat.no.sex.no.gender.no.age.no.ibd) #for all the rows and columns that are in the PHQ items at prepanline
           %in%
             phq.items_prepan]
        )
    )
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$na_per_person_phq_prepan) #have a look at the frequency

dat.no.sex.no.gender.no.age.no.ibd <- dat.no.sex.no.gender.no.age.no.ibd %>% #NA per person as a percentage
  mutate(
    miss_pc_total_phq_prepan = 
      na_per_person_phq_prepan/9 # NA per person divided by the amount of items
  )

freq(dat.no.sex.no.gender.no.age.no.ibd$miss_pc_total_phq_prepan)
```
